### 2025-04-27 paper/paper.tex
Update paper.tex

Research on traffic signal methods falls into three categories. These include single agent learning models, multi agent reinforcement learning models (MARL), and large-scale multi-agent learning models, with the large-scale MARL actively having new deep learning models applied in recent research.

\subsection{Single Agent Learning Models}

Before 2010, traffic prediction models were designed using single agent reinforcement learning models. These models were used to predict the movement of traffic using a single system, meaning a single neural network predicted how traffic lights should function. While innovative, they are generally not scalable for multiple intersections and can more effectively be used to predict how traffic signals function at a single intersection. These models were rarely used in practice and traffic signals used fixed intervals (threshold signaling) \cite{1}. As a result, we will not focus too much on these for our traffic problem.

\subsection{Multi Agent Learning Models}

@@

During this research period, the majority of models used a variation of Q-Learning. While not perfect, there were indications that there were improvements in terms of moving traffic over traditional timer methods. \cite{2} Eventually, a distributed MARL signal was designed such that each agent may learn the environment independently and communicate the signals it received to nearby agents to improve performance. This further came with the benefit of allowing one agent to fail without taking other agents down, increasing reliability and scalability \cite{5}. This innovation led to major improvements that have influenced the modern design of reinforcement learning techniques for traffic signal control.

@@

Since 2019, research indicates that MARL agents have been improved for scalability, performance, real-world applications and become open-source. The field has seen enormous growth from the initial small scale solutions, and large scale implementations for real world cities continue to become more practical and powerful.

Early breakthroughs in large-scale MARL focused on a more difficult problem: urban traffic management. This initially came with a new open sourced model, CityFlow, a multi-agent reinforcement model which could handle large road networks with thousands of intersections in a simulated environment \cite{7}. These large-scale models have shown significant improvements in performance while working at a larger scale, making them more adaptable to real situations.

In recent years, strong reinforcement learning models, such as long short-term memory (LSTM) and spatiotemporal graph convolutional neural networks (STGCN) have been applied to research, and external factors like pedestrian movements have begun being addressed. These advancements show more promise in scalability and performance, but are still in progress. There are still opportunities to test different models which may perform better in synchronization with other agents. While accounting for pedestrians marks a major step in optimizing the traffic signal problem, it opens more questions, such as how can we account for emergency vehicles, namely ambulances or police cars, or collisions that disturb the natural flow of traffic. Despite these questions, these models are very powerful in comparison to previous threshold traffic signal management systems.

@@

\section{Chronological Overview}
Based on the major research contributions, we have concluded that the papers fall into several categories. These categories tend to reflect the time period of the research contribution, with older papers using less-powerful Q-Learning simulations, and more recent papers using more powerful neural networks with account for more factors. Figure 2 highlights a chronological overview of the categorization of papers over time.

@@

Another research gap is regards real-world application. Several large cities have adapted deep learning techniques for traffic signal processing, though a large majority of cities do not yet have these technologies implemented. Therefore, they could see a change in performance depending on the size of the city and their road systems.

@@

However, there are a variety of challenges with implementation. One challenge is the difficulty in finding optimal Q values as there is no ground truth to compare it to, the agent has to guess and learn on the experience and rewards it receives. This method is also very computationally challenging, as the agent has to constantly update the Q-value, especially with very large and complex models. There is also difficulty in balancing exploration vs exploitation, if the agent explores too much, then the Q-value may not converge to its optimal value, and if it exploits what it knows too much then the value may get stuck at a suboptimal level. Solving this would require understanding and the use of certain exploration strategies. There are also problems that could arise with the environment. The environment can slowly change overtime, so our Q-value may become irrelevant, so the agent would have to relearn its environment. There are also many unexpected situations that may arise that may require the model to quickly learn and adapt in the unknown situation, or try to reinforce the model to account for these situations.

@@

After starting implementation, we decided that CityFlow was not the appropriate tool for this problem, despite our research. While a powerful tool, it struggled to handle the data format provided from OSM data, resulting in slow performance and broken intersections. We then decided moving to the SUMO simulator was a more worthwhile decision, as its efficiency has improved over time and documentation is more appropriate for our specific research area.

Once SUMO was installed, we downloaded public data for the city of Starkville Mississippi's road structure using the tool open street map, and used SUMO's netedit to process the data into a usable format. Some changes were made, such as fixing traffic signal placement using junctions and fixing non-signal-based intersection interactions.

Our ultimate goal with this project is to test how neural network influenced traffic signals direct the flow of traffic, so we needed to setup various simulation environments to simulate realistic traffic scenarios within Starkville. To do this, we used SUMO's built in flow generator, with various parameters to result in light, medium, and intense traffic scenarios. This would allow us to test how each method of traffic signal control reacts to various events such as morning and afternoon rush hours, post game traffic, or light summer traffic.

Using the configuration file, we can use the SUMO GUI, which comes included with the SUMO installation package. This tools allows us to run a visualization of the simulation with regards to the currently implemented method of traffic signal control, and make observations from the point of view of drivers without quantitative analysis, making observations about our model to make improvements. a

@@

In order to properly evaluate the performance of threshold and neural network models, a method of evaluation was needed beyond qualitative methods, such as observation or review. As a result we implemented various benchmarks to quantitatively decide the quality of a methods approach.

Our first method of benchmark involves calculating the average waiting time of a vehicle. This is the most likely representation of how frustrated one might feel. A lower waiting time is therefore a great benchmark, as it shows that traffic is moving and drivers are less likely to get frustrated and develop road rage or get into an accident.

The next is the average trip time. Because we will benchmark similar environments, we can get the average trip times of all combined vehicles in a simulation, and use it as a quantitative performance metric. Faster trips indicate a successful implementation of traffic signal control, as people can get to their end destination faster. It also serves as a benchmark for other metrics, likely indicating shorter queue lengths, less stops, and less time waiting at stops on average.

@@

Because there are several benchmarks, we will consider our model successful if any evaluation metric improves without a meaningful reducing another metric. For example, if average trip time decreases, but the other metrics remain very similar to their threshold results, we will consider the model a success.

@@

Our decentralized multi‐agent reinforcement learning (MARL) architecture is built around three key components: the Q‐network itself, a Deep Q-Network(DQN)‐based agent wrapper (complete with replay buffer and learning logic), and a SUMO–TraCI environment interface that supplies state and reward information every control interval. Traci allows us to easily modify our simulation and get state information from within the current timestep, while PyTorch allows us to efficiently build and implement our neural networks. This implementation lacks a central coordinator. Each agent acts on its own in coordination with other agents. The agents were designed to represent an intersection with a traffic signal controller, and could accept the state of the lanes leading to the intersection, the state of the signals, and the states of vehicles at each intersection such as stopped time. We define the neural network in models.py as a simple multilayer perceptron. Given an input dimension equal to the total number of lanes feeding into a signalized intersection and an output dimension equal to the number of possible signal phases, we stack two hidden layers of configurable width (48 units each in our experiments) with ReLU activations, and terminate with a linear layer producing a Q‐value for each phase.

Concretely, the helper function
\begin{verbatim}
build_mlp(input_dim, output_dim, hidden_layers):
    layers   = []
    prev     = input_dim
    for h in hidden_layers:
        layers.append(nn.Linear(prev, h))
        layers.append(nn.ReLU())
        prev = h
    layers.append(nn.Linear(prev, output_dim))
    return nn.Sequential(*layers)
\end{verbatim}
constructs the sequential network, allowing us to easily swap hidden‐layer sizes or depths via configuration.

Each intersection is managed by an instance of {\tt DQNAgent} (in policies.py), which maintains both an \emph{online} network and a \emph{target} network. At initialization, we load the target’s weights from the online network, and set up an Adam optimizer (learning rate 0.001), a discount factor $\gamma=0.99$, and an $\varepsilon$‐greedy exploration schedule that decays $\varepsilon$ from 1.0 to 0.05 by a factor of 0.995 per learning step. Experiences are stored in a fixed‐capacity deque buffer (size 5,000), and we sample mini‐batches of 32 transitions once the buffer is sufficiently large. In each learn() call we compute the predicted Q‐values for state–action pairs, form TD‐targets via \(Q_{\mathrm{target}} = r + \gamma (1 - d)\max_{a'} Q_{\mathrm{target}}(s', a')\) and minimize the mean‐squared error between predictions and targets. After each gradient update we decay $\varepsilon$, and every 100 updates we synchronize the target network with the online network. To scale this to multiple intersections, we wrap several {\tt DQNAgent} objects in {\tt MultiDQNAgent}, forwarding action selection, memory storage, and learning calls independently to each agent.

On the environment side (multi\_env.py, subclassing BaseEnv), we employ the Python library TraCI (traffic control interface) to simulate traffic in Starkville, MS. Our initial plan was to predict the optimal states of every intersection with a traffic light in Starkville, MS, however, upon implementation we realized our available hardware and the time frame would not allow us to do this. Instead, we opted to only use what we decided were points of interest, or intersections where traffic is particularly heavy and prone to congestion. Most of these points were decided by considering the importance of the road, the typical time spent at intersections, and personal experience. This method ensures that we don't expend computational resources at intersections that either see little traffic or do fine managing traffic on their own. Doing so significantly decreases the computational requirements to run the model, and allows us to focus only on critical points. At startup we invoke traci.start with a step length of 0.1s and a control interval of 5s, disabling verbose logs to save overhead. We automatically collect, for each traffic‐light signal (TLS), the set of incoming lanes by inspecting traci.trafficlight.getControlledLinks. Every control step, get\_state() returns a list of queue lengths, i.e.\ the number of halting vehicles per lane, by calling traci.lane.getLastStepHaltingNumber on each lane. We then compute a scalar reward for each TLS as the negative sum of its queue lengths, which incentivizes the agents to minimize congestion. When step(actions) is called, we apply each agent’s chosen phase via traci.trafficlight.setPhase, advance the simulation by the control interval, and then return the new state, reward list, and a done flag (triggered when no vehicles remain).

The overall training loop lives in main.py, which begins by parsing our configuration file. This configuration specifies 500 training episodes, an agent name ``multi\_dqn,'' and all key hyperparameters (learning rate, $\gamma$, $\varepsilon$ schedule, hidden‐layer sizes, buffer and batch sizes, and target‐update frequency). For each episode, we reset the environment, then for up to 2,400 steps (equivalent to 0.75 hours of simulated time) we query the multi‐agent for actions, step the environment, store transitions, and trigger a learning update immediately. Episode returns (the sum of all TLS rewards) are logged each episode, and upon completion of training we save each agent’s weights to disk. A similar loop runs in evaluation mode (with greedy action selection and no learning) to report average performance over ten episodes.

@@

In order to evaluate our model we did two tests, a qualitative analysis, which involves viewing the simulation to compare the original simulation to the baseline, and quantitative analysis where benchmarks were ran to evaluate the model with numbers representing the time taken driving and length of queues. Both methods are critical to effective analysis of the model. While training involved generating various traffic scenarios, or events where cars start at one point and end at another point, our testing involves one scenario, which uses similar traffic patterns seen to training. Using a single traffic scenario allows us to make observations of threshold and neural network based signals. This ensures that while testing, each vehicle has takes the same route so we can observe how our traffic signal management system performs relative to other methods.

@@

The MARL Deep Q-learning model saw notable improvements in terms of responsiveness. When there was no signs of incoming traffic or lines in stopped lanes, it skipped the redundancy of changing the state of traffic lights resulting in a generally smoother flow of traffic. When it did change, it seemed intelligent, considering how long cars have been waiting along with how many cars were waiting. While our model did not allow collisions to be considered, the more continuous flow of traffic saw less emergency stops, and generally safer roads. Analysis also revealed that vehicles would often arrive at their destination sooner than their threshold counterparts, with less time spent on the road generally resulting in safer roads with less congestion.

There were some limitations of MARL Deep Q-learning despite its generally better analysis. Oftentimes, a light would not change for long periods of times to direct more intense traffic at the expense of shorter lines. This would generally result in shorter average drive lengths, with one drive taking exceptionally long. This was relatively controlled, however, with no cars getting completely stuck, and eventually being directed even if it took a minute. It was also important to choose the right intersections as points of interest, as intersections with little to no congestion would flip their signals the moment a car came to an intersection. It was generally better for areas with extremely light traffic to stick with threshold signals. For points like these, a potentially better option is sensor based traffic signal controllers, which use more concrete rules to change traffic, but make observations similar to our learning model to inform these decisions.

@@

While simple observations provide great insight to the performance of our model, numbers to support our observations are potentially more important. As mentioned earlier, we developed several benchmarks based on the results of a simulation. Each benchmark provides a real insight that indicates the performance of a traffic signal control method without the need to make observations.

@@

The other sources provide great insight, but might have had a smaller research impact. Despite this, they are still high-quality papers and can be used to help solve our problem. These are still critical to understand the problem at hand, and have a meaningful impact on development of our traffic prediction model.

>>>>

Research on traffic signal methods falls into three categories. These include single-agent learning models, multi-agent reinforcement learning models (MARL), and large-scale multi-agent learning models, with the large-scale MARL actively having new deep learning models applied in recent research.

\subsection{Single-agent Learning Models}

Before 2010, traffic prediction models were designed using single-agent reinforcement learning models. These models were used to predict the movement of traffic using a single system, meaning a single neural network predicted how traffic lights should function. While innovative, they are generally not scalable for multiple intersections and can more effectively be used to predict how traffic signals function at a single intersection. These models were rarely used in practice and traffic signals used fixed intervals (threshold signaling) \cite{1}. As a result, we will not focus too much on these for our traffic problem.

\subsection{Multi-agent Learning Models}

@@

During this research period, the majority of models used a variation of Q-learning. While not perfect, there were indications that there were improvements in terms of moving traffic over traditional timer methods. \cite{2} Eventually, a distributed MARL signal was designed such that each agent may learn the environment independently and communicate the signals it received to nearby agents to improve performance. This further came with the benefit of allowing one agent to fail without taking other agents down, increasing reliability and scalability \cite{5}. This innovation led to major improvements that have influenced the modern design of reinforcement learning techniques for traffic signal control.

@@

Since 2019, research indicates that MARL agents have been improved for scalability, performance, and real-world applications and become open-source. The field has seen enormous growth from the initial small-scale solutions, and large-scale implementations for real-world cities continue to become more practical and powerful.

Early breakthroughs in large-scale MARL focused on a more difficult problem: urban traffic management. This initially came with a new open-sourced model, CityFlow, a multi-agent reinforcement model which could handle large road networks with thousands of intersections in a simulated environment \cite{7}. These large-scale models have shown significant improvements in performance while working at a larger scale, making them more adaptable to real situations.

In recent years, strong reinforcement learning models, such as long short-term memory (LSTM) and spatiotemporal graph convolutional neural networks (STGCN) have been applied to research, and external factors like pedestrian movements have begun being addressed. These advancements show more promise in scalability and performance but are still in progress. There are still opportunities to test different models which may perform better in synchronization with other agents. While accounting for pedestrians marks a major step in optimizing the traffic signal problem, it opens more questions, such as how we can account for emergency vehicles, namely ambulances or police cars, or collisions that disturb the natural flow of traffic. Despite these questions, these models are very powerful in comparison to previous threshold traffic signal management systems.

@@

\section{Chronological Overview}
Based on the major research contributions, we have concluded that the papers fall into several categories. These categories tend to reflect the time period of the research contribution, with older papers using less powerful Q-learning simulations, and more recent papers using more powerful neural networks that account for more factors. Figure 2 highlights a chronological overview of the categorization of papers over time.

@@

Another research gap regards real-world application. Several large cities have adapted deep learning techniques for traffic signal processing, though a large majority of cities do not yet have these technologies implemented. Therefore, they could see a change in performance depending on the size of the city and their road systems.

@@

However, there are a variety of challenges with implementation. One challenge is the difficulty in finding optimal Q values as there is no ground truth to compare it to, the agent has to guess and learn from the experience and rewards it receives. This method is also very computationally challenging, as the agent has to constantly update the Q-value, especially with very large and complex models. There is also difficulty in balancing exploration vs exploitation, if the agent explores too much, then the Q-value may not converge to its optimal value, and if it exploits what it knows too much then the value may get stuck at a suboptimal level. Solving this would require understanding and the use of certain exploration strategies. There are also problems that could arise with the environment. The environment can slowly change over time, so our Q-value may become irrelevant, so the agent would have to relearn its environment. There are also many unexpected situations that may arise that may require the model to quickly learn and adapt to the unknown situation, or try to reinforce the model to account for these situations.

@@

After starting implementation, we decided that CityFlow was not the appropriate tool for this problem, despite our research. While a powerful tool, it struggled to handle the data format provided by OSM data, resulting in slow performance and broken intersections. We then decided moving to the SUMO simulator was a more worthwhile decision, as its efficiency has improved over time and documentation is more appropriate for our specific research area.

Once SUMO was installed, we downloaded public data for the city of Starkville Mississippi's road structure using the tool OpenStreetMap and used SUMO's netedit to process the data into a usable format. Some changes were made, such as fixing traffic signal placement using junctions and fixing non-signal-based intersection interactions.

Our ultimate goal with this project is to test how neural network-influenced traffic signals direct the flow of traffic, so we needed to set up various simulation environments to simulate realistic traffic scenarios within Starkville. To do this, we used SUMO's built-in flow generator, with various parameters to result in light, medium, and intense traffic scenarios. This would allow us to test how each method of traffic signal control reacts to various events such as morning and afternoon rush hours, post-game traffic, or light summer traffic.

Using the configuration file, we can use the SUMO GUI, which comes included with the SUMO installation package. This tool allows us to run a visualization of the simulation with regards to the currently implemented method of traffic signal control, and make observations from the point of view of drivers without quantitative analysis, making observations about our model to make improvements. a

@@

In order to properly evaluate the performance of threshold and neural network models, a method of evaluation was needed beyond qualitative methods, such as observation or review. As a result, we implemented various benchmarks to quantitatively decide the quality of a method's approach.

Our first method of benchmarking involves calculating the average waiting time of a vehicle. This is the most likely representation of how frustrated one might feel. A lower waiting time is therefore a great benchmark, as it shows that traffic is moving and drivers are less likely to get frustrated and develop road rage or get into an accident.

The next is the average trip time. Because we will benchmark similar environments, we can get the average trip times of all combined vehicles in a simulation, and use it as a quantitative performance metric. Faster trips indicate a successful implementation of traffic signal control, as people can get to their end destination faster. It also serves as a benchmark for other metrics, likely indicating shorter queue lengths, fewer stops, and less time waiting at stops on average.

@@

Because there are several benchmarks, we will consider our model successful if any evaluation metric improves without a meaningful reduction of another metric. For example, if the average trip time decreases, but the other metrics remain very similar to their threshold results, we will consider the model a success.

@@

Our decentralized multi‐agent reinforcement learning (MARL) architecture is built around three key components: the Q‐network itself, a Deep Q-Network(DQN)‐based agent wrapper (complete with replay buffer and learning logic), and a SUMO–TraCI environment interface that supplies state and reward information every control interval. Traci allows us to easily modify our simulation and get state information from within the current timestep, while PyTorch allows us to efficiently build and implement our neural networks. This implementation lacks a central coordinator. Each agent acts on its own in coordination with other agents. The agents were designed to represent an intersection with a traffic signal controller and could accept the state of the lanes leading to the intersection, the state of the signals, and the state of vehicles at each intersection such as stopped time. We define the neural network in models.py as a simple multilayer perceptron. Given an input dimension equal to the total number of lanes feeding into a signalized intersection and an output dimension equal to the number of possible signal phases, we stack two hidden layers of configurable width (48 units each in our experiments) with ReLU activations and terminate with a linear layer producing a Q‐value for each phase.

Concretely, the helper function
\begin{verbatim}
build_mlp(input_dim, output_dim, hidden_layers):
    layers   = []
    prev     = input_dim
    for h in hidden_layers:
        layers.append(nn.Linear(prev, h))
        layers.append(nn.ReLU())
        prev = h
    layers.append(nn.Linear(prev, output_dim))
    return nn.Sequential(*layers)
\end{verbatim}
constructs the sequential network, allowing us to easily swap hidden layer sizes or depths via configuration.

Each intersection is managed by an instance of {\tt DQNAgent} (in policies.py), which maintains both an \emph{online} network and a \emph{target} network. At initialization, we load the target’s weights from the online network and set up an Adam optimizer (learning rate 0.001), a discount factor $\gamma=0.99$, and an $\varepsilon$‐greedy exploration schedule that decays $\varepsilon$ from 1.0 to 0.05 by a factor of 0.995 per learning step. Experiences are stored in a fixed‐capacity deque buffer (size 5,000), and we sample mini‐batches of 32 transitions once the buffer is sufficiently large. In each learn() call we compute the predicted Q‐values for state–action pairs, form TD‐targets via \(Q_{\mathrm{target}} = r + \gamma (1 - d)\max_{a'} Q_{\mathrm{target}}(s', a')\) and minimize the mean‐squared error between predictions and targets. After each gradient update, we decay $\varepsilon$, and every 100 updates we synchronize the target network with the online network. To scale this to multiple intersections, we wrap several {\tt DQNAgent} objects in {\tt MultiDQNAgent}, forwarding action selection, memory storage, and learning calls independently to each agent.

On the environment side (multi\_env.py, subclassing BaseEnv), we employ the Python library TraCI (traffic control interface) to simulate traffic in Starkville, MS. Our initial plan was to predict the optimal states of every intersection with a traffic light in Starkville, MS, however, upon implementation, we realized our available hardware and the time frame would not allow us to do this. Instead, we opted to only use what we decided were points of interest, or intersections where traffic is particularly heavy and prone to congestion. Most of these points were decided by considering the importance of the road, the typical time spent at intersections, and personal experience. This method ensures that we don't expend computational resources at intersections that either see little traffic or do fine managing traffic on their own. Doing so significantly decreases the computational requirements to run the model, and allows us to focus only on critical points. At startup we invoke traci.start with a step length of 0.1s and a control interval of 5s, disabling verbose logs to save overhead. We automatically collect, for each traffic‐light signal (TLS), the set of incoming lanes by inspecting traci.trafficlight.getControlledLinks. For every control step, get\_state() returns a list of queue lengths, i.e.\ the number of halting vehicles per lane, by calling traci.lane.getLastStepHaltingNumber on each lane. We then compute a scalar reward for each TLS as the negative sum of its queue lengths, which incentivizes the agents to minimize congestion. When step(actions) is called, we apply each agent’s chosen phase via traci.trafficlight.setPhase, advance the simulation by the control interval, and then return the new state, reward list, and a done flag (triggered when no vehicles remain).

The overall training loop lives in main.py, which begins by parsing our configuration file. This configuration specifies 500 training episodes, an agent name ``multi\_dqn,'' and all key hyperparameters (learning rate, $\gamma$, $\varepsilon$ schedule, hidden‐layer sizes, buffer and batch sizes, and target‐update frequency). For each episode, we reset the environment, then for up to 2,400 steps (equivalent to 0.75 hours of simulated time) we query the multi‐agent for actions, step the environment, store transitions, and trigger a learning update immediately. Episode returns (the sum of all TLS rewards) are logged each episode, and upon completion of training, we save each agent’s weights to disk. A similar loop runs in evaluation mode (with greedy action selection and no learning) to report average performance over ten episodes.

@@

In order to evaluate our model we did two tests, a qualitative analysis, which involves viewing the simulation to compare the original simulation to the baseline, and a quantitative analysis where benchmarks were run to evaluate the model with numbers representing the time taken driving and length of queues. Both methods are critical to the effective analysis of the model. While training involves generating various traffic scenarios, or events where cars start at one point and end at another point, our testing involves one scenario, which uses similar traffic patterns seen in training. Using a single traffic scenario allows us to make observations of threshold and neural network-based signals. This ensures that while testing, each vehicle takes the same route so we can observe how our traffic signal management system performs relative to other methods.

@@

The MARL Deep Q-learning model saw notable improvements in terms of responsiveness. When there were no signs of incoming traffic or lines in stopped lanes, it skipped the redundancy of changing the state of traffic lights resulting in a generally smoother flow of traffic. When it did change, it seemed intelligent, considering how long cars had been waiting along with how many cars were waiting. While our model did not allow collisions to be considered, the more continuous flow of traffic saw fewer emergency stops, and generally safer roads. Analysis also revealed that vehicles would often arrive at their destination sooner than their threshold counterparts, with less time spent on the road generally resulting in safer roads with less congestion.

There were some limitations of MARL Deep Q-learning despite its generally better analysis. Oftentimes, a light would not change for long periods of time to direct more intense traffic at the expense of shorter lines. This would generally result in shorter average drive lengths, with one drive taking exceptionally long. This was relatively controlled, however, with no cars getting completely stuck, and eventually being directed even if it took a minute. It was also important to choose the right intersections as points of interest, as intersections with little to no congestion would flip their signals the moment a car came to an intersection. It was generally better for areas with extremely light traffic to stick with threshold signals. For points like these, a potentially better option is sensor-based traffic signal controllers, which use more concrete rules to change traffic but make observations similar to our learning model to inform these decisions.

@@

While simple observations provide great insight into the performance of our model, numbers to support our observations are potentially more important. As mentioned earlier, we developed several benchmarks based on the results of a simulation. Each benchmark provides a real insight that indicates the performance of a traffic signal control method without the need to make observations.

@@

The other sources provide great insight but might have had a smaller research impact. Despite this, they are still high-quality papers and can be used to help solve our problem. These are still critical to understanding the problem at hand and have a meaningful impact on the development of our traffic prediction model.
